\section{\textcolor{section_5}{Selected Projects}}
\vspace{-\baselineskip}
{
	\renewcommand{\arraystretch}{2}
	\renewcommand{\cellalign}{lt}
	% \setlength{\tabcolsep}{0.3cm}
	\begin{tabularx}{\textwidth}{@{}X p{0.20cm} r @{}}
		\textbf{photonLauncher} \hfill \badge{python/bash} \par \urllinkout{https://github.com/sunjerry019/photonLauncher}{github.com/sunjerry019/photonLauncher} \par {\scriptsize \color{gray} Measuring the Temporal Correlation of Light from a Mercury Discharge Lamp \hfill\texttt{2016}} & & \makecell{\texttt{\large 2019} \\ \texttt{\hfill \hspace{0.1mm} $\wedge$ \hfill} \\ \texttt{\large 2014}}\\[-0.5em]
		{\small Created equipment interfacing scripts used on Linux with \code{pyusb} and automated said scripts for repeated data acquisition. \code{numpy} and \code{gnuplot} were used to statiscally analyse collected data. Reverse \code{SSH} was utilized for remote monitoring, experimentation and extraction of data without physical access to the lab.} & & \\
		\textbf{Luggage Tags} \hfill \badge{C++} \par \textcolor{gray}{\small Singapore Armed Forces} & & \texttt{\large 2018}\\[-1em]
		{\small Modified \code{svg} files using \code{C++} to automate the generation of $>$ \nummer{1200} personalised luggage tags for an overseas exercise against time and manpower constraints. } & & \\
		\textbf{The English Tuition Corner} \hfill \badge{Full Stack} \par \urllinkout{http://theenglishtuitioncorner.com}{theenglishtuitioncorner.com} & & \texttt{\large 2017}\\[-0.5em]
		{\small Deployed a \code{Wordpress} website and email server for my teacher from a \code{LAMP} VPS. Emails were also properly authenticated with \code{DKIM} and \code{SPF}.} & & \\
	\end{tabularx}
}
\vspace{-\baselineskip}
\vspace{-0.5cm}

{
	\renewcommand{\arraystretch}{2}
	\renewcommand{\cellalign}{lt}
	% \setlength{\tabcolsep}{0.3cm}
	\begin{tabularx}{\textwidth}{@{}X p{0.20cm} r @{}}
		\textbf{SMB Redesigned} \hfill \badge{JS} \par \urllinkout{http://github.com/sunjerry019/SMB_Redesigned}{github.com/sunjerry019/SMB\_Redesigned} & & \texttt{\large 2016}\\[-0.5em]
		{\small \code{Greasemonkey} User Script that incorporated \code{MaterializeCSS} to create a custom, better designed user interface to the school's online message board {\footnotesize (SMB)} at its original endpoints.} & & \\
		\textbf{svg2eqn} \hfill \badge{python} \par \urllinkout{http://github.com/sunjerry019/svg2eqn}{github.com/sunjerry019/svg2eqn} & & \texttt{\large 2016}\\[-0.5em]
		{\small \code{Python} script that converts simple \code{svg} images into parametric equations that can be plotted on a graphing calculator. Used to submit entries for a graphing calculator design competition.} & & \\
		\textbf{CCA Website} \hfill \badge{HTML/CSS/JS} \par \urllinkout{https://github.com/sunjerry019/hci-cca-website}{github.com/sunjerry019/hci-cca-website} & & \texttt{\large 2015}\\[-0.5em]
		{\small Volunteered to deploy an infosite to my high school server to centralise CCA information for new students.} & & 
		% insert 24hr kayak
	\end{tabularx}
}