\vspace{-1em}
\section{\textcolor{section_5}{Selected Projects}}
\vspace{-\baselineskip}
{
	\renewcommand{\arraystretch}{1.9}
	\renewcommand{\cellalign}{lt}
	% \setlength{\tabcolsep}{0.3cm}
	\begin{tabularx}{\textwidth}{@{}X p{0.20cm} r @{}}
		\textbf{LatexBot} \hfill \badge{NodeJS} \par \urllinkout{https://github.com/sunjerry019/LatexBot}{github.com/sunjerry019/LatexBot} & & \texttt{\large 2020}\\[-0.5em]
		{\footnotesize Easily self-deployable Telegram Bot that renders \mylatex{} on-the-fly. Supports compiling directly on server with pre-installed TeXLive for better data protection.} & & \\
		\textbf{photonLauncher} \hfill \badge{python/bash} \par \urllinkout{https://github.com/sunjerry019/photonLauncher}{github.com/sunjerry019/photonLauncher} \par {\scriptsize \color{gray} Measuring the Temporal Correlation of Light from a Mercury Discharge Lamp \hfill\texttt{2016}} & & \makecell{\texttt{\large 2019} \\ \texttt{\hfill \hspace{0.1mm} $\wedge$ \hfill} \\ \texttt{\large 2014}}\\[-0.5em]
		{\footnotesize Setting up of lab infrastructure from scratch. Created equipment interfacing scripts on Linux and automated data acquisition. Remote monitoring, experimentation and extraction of data without physical access to the lab was set up. Basic Linux system administration.} & & \\
		\textbf{OneCorpSec} \hfill \badge{python/Full Stack} \par \urllinkout{https://github.com/sunjerry019/onecorpsec}{github.com/sunjerry019/onecorpsec} & & \texttt{\large 2019}\\[-0.5em]
		{\footnotesize Automated Corporate Secretary System written in \code{Django}. Freelance Work. Database with an web administration front-end that periodically sends out reminder E-Mails to various stakeholders based on pre-set conditions. } & & \\
		\textbf{The English Tuition Corner} \hfill \badge{Full Stack} \par \urllinkout{https://theenglishtuitioncorner.com}{theenglishtuitioncorner.com} & & \texttt{\large 2017}\\[-0.5em]
		{\footnotesize Deployed a \code{Wordpress} website and email server for my teacher from a \code{LAMP} VPS. Emails were also properly authenticated with \code{DKIM} and \code{SPF}.} & & \\
% 	\end{tabularx}
% }
% \vspace{-\baselineskip}
% \vspace{-0.5cm}

% {
% 	\renewcommand{\arraystretch}{1.9}
% 	\renewcommand{\cellalign}{lt}
% 	% \setlength{\tabcolsep}{0.3cm}
% 	\begin{tabularx}{\textwidth}{@{}X p{0.20cm} r @{}}
		% \textbf{SMB Redesigned} \hfill \badge{JS} \par \urllinkout{http://github.com/sunjerry019/SMB_Redesigned}{github.com/sunjerry019/SMB\_Redesigned} & & \texttt{\large 2016}\\[-0.5em]
		% {\small \code{Greasemonkey} User Script that incorporated \code{MaterializeCSS} to create a custom, better designed user interface to the school's online message board {\footnotesize (SMB)} at its original endpoints.} & & \\
		% \textbf{svg2eqn} \hfill \badge{python} \par \urllinkout{http://github.com/sunjerry019/svg2eqn}{github.com/sunjerry019/svg2eqn} & & \texttt{\large 2016}\\[-0.5em]
		% {\small \code{Python} script that converts simple \code{svg} images into parametric equations that can be plotted on a graphing calculator. Used to submit entries for a graphing calculator design competition.} & & \\
		% \textbf{CCA Website} \hfill \badge{HTML/CSS/JS} \par \urllinkout{https://github.com/sunjerry019/hci-cca-website}{github.com/sunjerry019/hci-cca-website} & & \texttt{\large 2015}\\[-0.5em]
		% {\small Volunteered to deploy an infosite to my high school server to centralise CCA information for new students.} & & 
		% insert 24hr kayak
	\end{tabularx}
}